\titledquestion{Traffic Network}[8]

In SC101 country, there are $n$ cities and $m$ \textbf{broken} roads, with each broken road connecting two different cities. You can consider this as a graph $G=(V, E)$.

Now the government wants to build a traffic net in the SC101 country. There are $2$ crucial steps to take in constructing this traffic network:
\begin{enumerate}
    \item Establish an airport in the $i$-th city with a cost of $a_i$
    \item Repair the broken road $e_j = (u_j, v_j)$ to connect the city $u_j$ and $v_j$, cost $b_j$.
\end{enumerate}
In the final network, every city will either have an airport or be connected to a city with an airport. Your task is to design an algorithm to find the minimum cost to build the network.

\textbf{Hint:} You may find that the sum of the number of airports to be built and the number of roads to be repaired is $n$.

\begin{solution}
    \begin{enumerate}
        \item Since there must be at least one airport, thus build an airport at the kth city whose $a_k$ is the lowest among $a_i$. Remove $a_k$ from the set.
        \item Building an airport at a city is the same with constructing a edge between either of other cities with airport.
              Thus merge set A(the cost of airports) and B(the cost of roads) and sort the new set into ascending order.
        \item Using Kruskal's Algorithm to choose whether road or airport should be construct.
              If there are airports and roads to connect two cities, it construct a cycle.
        \item Repeat the operations above till all the elements in the new set are visited.
    \end{enumerate}
\end{solution}