\titledquestion{Noise}[6]

The road of SC101 country is represented by an undirected graph $G = (V, E)$ and each vertex represents a city or an airport. The set of airports is represented by $T \subset V$.

A vertex $v$ is said to \textit{be effected by noise} from an airport $t$ if the length of the shortest path from $t$ to $v$ is not larger than $R$. We want to find all the vertices that have noise.

Please design an algorithm to solve this question. You may call any algorithm learned in lecture as a subroutine but be sure to indicate its input. You \textbf{don't} need to prove the correctness of your algorithm. Then, analyze your \textbf{time complexity}.

To get full credits, the time complexity of your algorithm should not exceed $O\left(\left(|V| + |E|\right) \log |V|\right)$.

\textbf{Input:}
\begin{itemize}
    \item $G = (V, E)$, where $V=\{1,2,\ldots, n\}$, $E=\{(u_i,v_i,w_i):i=1,2,\ldots, m\}$, $w_i > 0$
    \item $T = \{t_1, \ldots, t_{l}\}$, where $|T| = l$, $1 \le t_i \le n$
    \item A positive number $R$
\end{itemize}

\textbf{Output:} All vertices $v$ that are effected by noise from \textbf{at least one} airport $t \in T$.


\begin{solution} \\
    Use Dijkstra's algorithm to solve this problem.
    \begin{enumerate}
        \item Set the airports has the 0 distance and other cities has $\infty$ distance. Use adjacency list to restore the distance and use min-heap to choose which to visit.
        \item Pop the top element of the min-heap and traverse its neighbour, renew their distance if the new distance is lower than its past distance.
        \item Repeat the operations above until there is no vertex in the min-heap.
        \item Traverse the vertices set and output all vertices with distance less than R.
    \end{enumerate}
    Time complexity analysis: \\
    First we should build a min-heap of vertex with distance, which is O(VlogV), and traverse the set T to set the distance of airports to 0, which is O(V).
    Then for every vertex to be removed, we should find all his neighbour, thus the complexity will be O(E) $\cdot$ O(logV).
    So that the whole time complexity is O(VlogV+ElogV).
\end{solution}




